---
title: "p8105_hw5_as5457"
author: "Sunny Siddique"
date: "November 7, 2018"
output: github_document
---

```{r}
library(tidyverse)
```

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.


```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
```

Trying to import the dataset.
```{r}
list.files("./data")
```

There are 20 datafiles. 

```{r}
files <- list.files("./data")
files
```

```{r}
raw = str_c("./data/", files)
datasets = tibble(subjects = files) %>% 
  mutate(data = map(raw, read_csv))
raw
```

