---
title: "Homework 5 - Data Science I"
author: "Sunny Siddique"
date: "November 7, 2018"
output: github_document
---

**Problem 1: Analysis of a longitudinal study data that contains a treatment arm and a placebo arm.**


```{r message = F}
#Setting global parameters and loading relevant packages
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
```

In attempting to import the dataset, I am first using the list.files function to view the files for the study participants. There are 20 different files (10 containing data for individuals in the treatment arm and 10 containing data for individuals in the control arm).
```{r}
#Creating a new object "files" to which to store the datafiles.
files = list.files("./data")
files
```

```{r message = F}
#Saving the datafiles into raw list and then assigning it to "datasets".
raw = str_c("./data/", files)
datasets = tibble(subjects = files) %>% 
  mutate(data = map(raw, read_csv))
datasets
```

In order to tidy up the dataset, I took the following steps:

```{r}
#Assigning the tidy dataset into "participants" 
participants = unnest(datasets) %>% 

#Separating the subject variable into treatment "arm" and participant "id" variable.
  separate (subjects, into = c("arm", "id"), sep = "_") %>% 
  
#Separating the id varaible into "participant_id" and a variable called "remove" that will be dropped later. 
  separate (id, into = c("participant_id", "remove"), sep = 2) %>% 
  
#Dropping the "remove" variable
  select (-remove) %>% 
  
#Gathering the week variables under one column. 
  gather (key = week, value = observation, week_1:week_8) %>% 
  
#Tidying the week variable. 
  separate (week, into = c("remove", "week"), sep = "_") %>% 
  
#Removing the extra column
  select (-remove)

#Viewing the resulting dataset. 
head(participants)
```

Making a spaghetti plot showing observations on each subject over time.

```{r}
#Naming the spaghetti plot, "spaghetti"
spaghetti = participants %>% 
  
#Converting the participant_id into a character variable and the treatment arm varible into a factor variable to be able to piece together the spaghetti plot. 
  mutate(participant_id = as.character(participant_id),
         arm = as.factor(arm)) %>% 
  
#Generating spaghettiplot using ggplot. 
  ggplot(aes(x = week, y = observation, color = participant_id, group = participant_id)) +
  geom_point() + 
  geom_line() +
  facet_grid(~arm) +
  labs (
    title = "Time-trends of participants' condition",
        x = "Week",
        y = "Observation"
  )

#Viewing the spaghetti plot. 
spaghetti
```

In the spaghetti plot above, it appears that with time, the observation values for those in the experimental group appeared to increase whereas for those in the control group, the observation values remained approximately the same. Even though in the experimental group, there are small fluctuations each week, their overall trend seems to be increase with time. 

-------------------------------------------------------------
**Problem 2: Analysis of homicide data in 50 large US cities, by the Washington Post.**


```{r}
#Reading in the dataset
homicide_data = read_csv("./homicide-data.csv") %>% 
  janitor::clean_names()
```

This the dimension of this raw dataset is `r dim_desc(homicide_data)`. The rows of the dataset contain information regarding each individual convicted of homicide. There are a number of variables included regarding the convicted individual, including their name, race, age, sex, city, state and the decision of their case (disposition). 

Create a city_state variable and then summarizing within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
#Creating a new dataset called homicide_totals
homicide_totals = homicide_data %>% 
  
#Creating the "city_state" variable by concatenating city and state variables.
  mutate(city_state = str_c(city, state, sep = ", ")) %>% 
  
#Filtering out Tulsa, AL because it appears that it's latitute and longitude does not exist (from discussion board question)
  filter(city_state != "Tulsa, AL") %>% 
  
#Making 50 groups by city_state variable. 
  group_by(city_state) %>% 
  
#Nesting within a larger list. 
  nest() %>% 
  
#Creating new variables that will map total_homicides and total_unresolved cases. 
  mutate (total_homicides = map(.x = data, ~.x %>% count()),
          total_unsolved = map(.x = data, ~.x %>% 
          filter(disposition %in% 
            c("Closed without arrest","Open/No arrest")) %>% 
                                 count())) %>% 

#Selecting relavant variables.
  select(city_state, total_homicides, total_unsolved) %>% 
  
#Unnesting to create individual dataframes.
  unnest() %>% 
  
#Changing the names from n to more descriptive column names.
  mutate(total_homicides = n, total_unsolved = n1)

#Creating a final tidy dataset by removing extra columns. 
homicide_total = homicide_totals %>% 
  select(-n, -n1)

#Viewing the final dataset.
homicide_total
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_data = homicide_total %>% 
  filter (city_state == "Baltimore, MD")

#filtering out data for baltimore. 

baltimore_proptest = 
  prop.test(baltimore_data$total_unsolved, baltimore_data$total_homicides) %>% 
  broom::tidy()
baltimore_proptest
```

```{r}
balt_proptest = broom::tidy(prop.test(baltimore_data$total_unsolved, baltimore_data$total_homicides)) %>% 
  select(estimate, conf.low, conf.high)
```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and  unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
homicide_function = map2(.x = homicide_total$total_unsolved, .y = homicide_total$total_homicides, ~ prop.test(.x, .y))

all_proptest = map_df(.x = homicide_function, ~.x %>% 
                        broom::tidy(.x) %>% 
                        select(estimate, conf.low, conf.high)) %>% 
  mutate(city_state = homicide_total$city_state) %>% 
  select(city_state, everything())

homicide_data %>% 
  select(city, state) %>% 
  group_by(city, state)
```


Plotting the variables
```{r}
all_proptest %>% 
  mutate(city_state = forcats::fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + geom_point() +
  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

