---
title: "p8105_hw5_as5457"
author: "Sunny Siddique"
date: "November 7, 2018"
output: github_document
---

```{r}
library(tidyverse)
```

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.


```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
```

Trying to import the dataset.
```{r}
list.files("./data")
```

There are 20 datafiles. 

```{r}
files <- list.files("./data")
files
```

```{r}
raw = str_c("./data/", files)
datasets = tibble(subjects = files) %>% 
  mutate(data = map(raw, read_csv))
datasets
```

Let's try to tidy the dataset
```{r}
participants = unnest(datasets) %>% 
  separate (subjects, into = c("arm", "id"), sep = "_") %>% 
  separate (id, into = c("participant_id", "remove"), sep = 2) %>% 
  select (-remove) %>% 
  gather (key = week, value = observation, week_1:week_8) %>% 
  separate (week, into = c("remove", "week"), sep = "_") %>% 
  select (-remove)
participants
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
spaghetti = participants %>% 
  mutate(participant_id = as.integer(participant_id),
         arm = as.factor(arm)) %>% 
  ggplot(aes(x = week, y = observation, color = arm, group = participant_id)) +
  geom_point() + 
  geom_line() +
  facet_grid(~arm)
spaghetti
```

problem 2

Reading in the homicide dataset

```{r}
homicide_data = read_csv("./homicide-data.csv") %>% 
  janitor::clean_names()
```

#Describe the raw data. 

Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide_data %>% 
  mutate(city_state = str_c(city, state, sep = ", ")) %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate (total_homicides = map(.x = data, ~.x %>% count()))
```

