---
title: "Homework 5 - Data Science I"
author: "Sunny Siddique"
date: "November 7, 2018"
output: github_document
---

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.


```{r message = F}
#Setting global parameters and loading relevant packages
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
```

In attempting to import the dataset, I am first using the list.files function to view the files for the study participants. There are 20 different files (10 containing data for individuals in the treatment arm and 10 containing data for individuals in the control arm).
```{r}
#Creating a new object "files" to which to store the datafiles.
list.files("./data")
files = list.files("./data")
files
```

```{r}
raw = str_c("./data/", files)
datasets = tibble(subjects = files) %>% 
  mutate(data = map(raw, read_csv))
datasets
```

Let's try to tidy the dataset
```{r}
participants = unnest(datasets) %>% 
  separate (subjects, into = c("arm", "id"), sep = "_") %>% 
  separate (id, into = c("participant_id", "remove"), sep = 2) %>% 
  select (-remove) %>% 
  gather (key = week, value = observation, week_1:week_8) %>% 
  separate (week, into = c("remove", "week"), sep = "_") %>% 
  select (-remove)
participants
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
spaghetti = participants %>% 
  mutate(participant_id = as.character(participant_id),
         arm = as.factor(arm)) %>% 
  ggplot(aes(x = week, y = observation, color = participant_id, group = participant_id)) +
  geom_point() + 
  geom_line() +
  facet_grid(~arm)
spaghetti
```

problem 2

Reading in the homicide dataset

```{r}
homicide_data = read_csv("./homicide-data.csv") %>% 
  janitor::clean_names()
```

#Describe the raw data. 

Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide_totals = homicide_data %>% 
  mutate(city_state = str_c(city, state, sep = ", ")) %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate (total_homicides = map(.x = data, ~.x %>% count()),
          total_unsolved = map(.x = data, ~.x %>% 
                                 filter(disposition %in% c("Closed without arrest","Open/No arrest")) %>% 
                                 count())) %>% 
  select(city_state, total_homicides, total_unsolved) %>% 
  unnest() %>% 
  mutate(total_homicides = n, total_unsolved = n1)
homicide_total = homicide_totals %>% 
  select(-n, -n1)
homicide_total
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_data = homicide_total %>% 
  filter (city_state == "Baltimore, MD")

#filtering out data for baltimore. 

baltimore_proptest = 
  prop.test(baltimore_data$total_unsolved, baltimore_data$total_homicides) %>% 
  broom::tidy()
baltimore_proptest
```

```{r}
balt_proptest = broom::tidy(prop.test(baltimore_data$total_unsolved, baltimore_data$total_homicides)) %>% 
  select(estimate, conf.low, conf.high)
```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and  unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
homicide_function = map2(.x = homicide_total$total_unsolved, .y = homicide_total$total_homicides, ~ prop.test(.x, .y))

all_proptest = map_df(.x = homicide_function, ~.x %>% 
                        broom::tidy(.x) %>% 
                        select(estimate, conf.low, conf.high)) %>% 
  mutate(city_state = homicide_total$city_state) %>% 
  select(city_state, everything())

homicide_data %>% 
  select(city, state) %>% 
  group_by(city, state)
```


Plotting the variables
```{r}
all_proptest %>% 
  mutate(city_state = forcats::fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + geom_point() +
  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

